Introduction

### 2022-02-19 Manuscript/Manuscript_Discussion.Rmd
English proof reading and better number formatting

We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
This framework implements standard approaches and uses ad-hoc solutions to deal with common SRA issues.
By freely sharing the tool as an open-source R package and by following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
The framework consists of four main components: 1) an integrated query-based citation search and management engine, 2) a Bayesian active machine learning-based citation classifier, and 3) a data-driven search query generation algorithm.\

The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e., Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the two more (SCOPUS, EMBASE) databases.
In comparison, most SRH tools, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing just on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
Mixing different databases is fundamental to have a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
in our results, 18.7% of the positive matches found only in one of the different data sources, and no positive record was present in all of them (data not shown).\
The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of online citation databases in terms of traffic and download quotas.
The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
The preliminary ordering allows to increase the positivity rate in the initial training set [@wallace2010active].\

For the framework's record classification module, we employed an active machine learning approach [@settles2009active, @miwa2014reducing] based on the best practices from other SRA studies but also bringing further improvements at various levels.\
The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform text into input data for machine learning.
We did not include classical n-grams [@schonlau2017text], but we used network analysis to find non-consecutive frequently associated terms, a generalisation of n-grams relaxing the term adjacency assumption.
This approach allows also to find term connections across fields, for example a term having a different relevancy if associated with a specific author.
The same technique but with different parameters was applied to merge redundant terms to make model estimation more efficient and reduce noise.\
The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text; @ohsawa1998keygraph] and is a valuable tool to extract semantic information not evident in one-word or consecutive n-gram models.\

The automatic classification algorithm is based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine].
As with other boosted trees algorithms [@hastie2009boosting], BART can explore complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.\
However, its Bayesian foundation provides further benefits:
less sensitivity on hyperparameter choices, natural regularisation through priors, and, especially, predictive distributions as output in place of point-wise predictions [@soria2011belm; @joo2020being; @jospin2020hands].
By selecting relatively tight prior distributions, we discouraged excessively deep trees, long sequences of trees, or extreme predicted probabilities, to decrease the risk of overfitting.\
The algorithm runs multiple replications of the model and averages their predictive distributions creating an "ensemble";
this technique has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble], as we were able to confirm during the hyperparameter evaluation (Supplemental Material S2).
Ensembling reduces the uncertainty in the predictive distribution tails related to the randomness in the MCMC fit [@robert2004monte], generating a shift of probability mass towards the distribution centre and stabilising it (i.e., decreasing variance without impacting bias).
On the other hand, just imposing robust uninformative priors against extreme predictions would have decreased variance but also shifted the distribution towards a non-decision zone, increasing bias [@hansen2000bayesian].\
Since the number of model replications significantly impacts computation times, we decided to use ten replicas, the lower value after which performance stabilised during the hyperparameter evaluation.\
We also investigated whether bootstrapping between replications [@breiman1996bagging] would improve performance, but, contrary to theory [@diez2015diversity], it appeared to be slightly detrimental in our case (Supplemental Material S2) compared to simple ensembling.\

A low rate of relevant matches (class imbalance) is typical in literature reviews [@sampson2011precision; @wallace2010semi; @o2015using], and such strong imbalance between positive and negative records can affect sensitivity [@khoshgoftaar2010comparing; @chawla2004special].\
To overcome the problem, we oversampled [@batista2004study] the positive records ten times before model fitting.
Our hyperparameter analysis showed that together with model ensembling, the oversampling rate was the parameter with the highest impact on performance.\
A known risk with positive oversampling is the misclassification of negative records [@ramezankhani2016impact].
However, since all predicted positives get manually reviewed in our approach, we are always ensured to achieve 100% specificity/positive predictive value: the only price for the increased sensitivity due to oversampling is a larger number of records to review.\
An alternative to oversampling would be applying different weights and/or cost to the classes [@abd2013review; @diez2015diversity], but the BART implementation we used did not have this feature;
also, using simple oversampling permits broader compatibility with different modelling engines [@galar2011review; @roshan2020improvement].\
Finally, ordering the records by query term frequency (simple query ordering) generates a far higher rate of relevant records in the initial training set (17.2%) compared to the overall data (0.11%), and this boosts the sensitivity of the model.\

One of the central innovations we introduced is the concept of "uncertainty zone", whose implementation is possible thanks to the Bayesian foundation of the classification model.
This construct guides the selection of the records to review, dynamically updating and shrinking after every CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig. 1).\
This approach overcomes the usual requirement of dataset-specific hard thresholds in active machine learning, and also allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
The parameters our algorithm needs are instead general and non task-specific, like the PPD intervals based on which the uncertainty zone is built, and the maximum number of iterations with no positive matches after which a session is concluded;
the hyperparameter evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to perform well on most datasets.\
Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\

We evaluated performance as the capability of the screening procedure (automatic classification plus manual review) to find the largest number of relevant records while reviewing as few of them as possible (i.e., sensitivity $\times$ efficiency).\
We avoided the classic out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study; @james2013introduction].
Such methods primarily assume that the rate of positivity is equal on average in every random subset of the data [@tashman2000out];
this uniformity is broken by how the initial training set and the subsequent reviewed records are selected by the query-based ordering and the active learning algorithm, determining a lower positivity rate in the unlabelled records (Fig. 2).
Also, a literature corpus is unique per search query/database combination, and therefore any out-of-sample performance estimate is not replicable since no new data can be acquired related to the current corpus.\
Instead, to estimate overall sensitivity, we employed simple Bayesian regression (surrogate model) on the manually reviewed data to abstract the classification model predictions and achieve a maximum entropy [@harremoes2001maximum] estimate of the number of missed positive matches among the unreviewed records in the whole dataset.
This simple surrogate model fitted the data very well ($R^2$ consistently above 97%) using just the lower 98% PrI bound of the PPDs as predictor, indicating predictive consistency in the classification model.
The surrogate model posterior predictive distribution could be exploited to explore worse case scenarios in terms of sensitivity.\

Our framework achieved very high sensitivity by screening a markedly small fraction of all records, bringing a sensible reduction in workload.\
Based on the surrogate model, we predicted a predicted median sensitivity of 100% [93.5%, 100%] in the first session (screening 4.29% of records) and of 97.3% [73.8%, 100%] in the second (screening 1.34% of records):
efficiency increased significantly in the second session since only a few new positive matches were found, but given the large number of records, uncertainty regarding sensitivity also expectedly increased.\
Both results are above the usual performance in the field [@o2015using] and in line with the 92% average sensitivity estimated after human-only screening [@edwards2002identification].
In one interesting case, the model spotted a human-made misclassification error, demonstrating its robustness and value as a second screener, a role already suggested for SRA tools by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].
Finally, albeit the simple query ordering already concentrated most of the relevant matches in the first 20-25 thousand records, without the tool support some relevant records would have required almost the complete data set to be manually checked to be found.\

The model took ~5-20 minutes per iteration to perform predictions in session 1 (17,755 documents) and 20-40 minutes in session 2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM laptop from 2014;
including manual record review, one session required 1-3 days of work, for a total of 1-2 weeks for the whole process (including record collection).
That is a considerable saving of time compared to the multiple months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating].
To our knowledge, the amount of data processed (~100.000 records) were larger than what is typical in most SRA studies [@o2015using; @olorisade2016critical], emphasising the reliability of the tool in real-world scenarios.\

The last module of our framework is a data-driven query generation algorithm.
Creating an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching];
it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of records to review.
Our solution joins a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD, with a human review step and an efficiency-driven query builder.
The aim is to generate a second query that helps find records missed during the first session search.
The generated query allowed indeed to retrieve few more positive matches not found in session 1, but at the cost of a significant increase in the number of documents.\
One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules learned by the classification model, showing which combination of terms was particularly relevant and even spotting authors and geographical locations associated with the study topic.
The generated query, therefore, acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to understand and spot bias in black-box classification algorithms [@malhi2020explainable];
explainability is often required or even legally mandatory for high-stake machine learning applications [@bibal2021legal; @bibal2020impact].\
It is important to note that this process is entirely data-driven.
The algorithm is only aware of the "world" defined by the data set used as input, which is generated by a specific search query focused on a particular topic.
Therefore, the new query may not be specific enough once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
The solution we found was to add another component to the query, specifying the general topic (antimicrobial resistance and healthcare-associated infections) of our research.\

As reported, our framework builds on modularity.
We designed it to easily implement complete independence of the main modules in future iterations, making it possible for users to add custom features like citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
We deem such interoperability extremely relevant because the main strength of our tool is the composition of many solutions and the general idea of Bayesian active machine learning and the exploit of the derived uncertainty in predictions.
However, each of its components could benefit considerably from the recent improvements in text mining.\
For example, our text processing approach is quite simple, based on the boolean bag-of-words paradigm, and indeed could be improved by more nuanced text representations.
It could be evaluated if feature transformations like TF-IDF [@baeza1999modern; @ananiadou2006text] would be advantageous, even if we hypothesise that tree-based classification algorithms like BART are robust enough not to need such operations.
Word embedding could be instead worth exploring:
this technique transforms terms in semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep] and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context.
Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] or graph-of-word techniques [@ohsawa1998keygraph; @rousseau2015graph] to extract topics to enrich the feature space.\
Our classification algorithm can be implemented with any Bayesian supervised machine learning method that provides full PPDs;
therefore alternative classification models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian].
Even more interesting would be to test advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher-level features in the text like term context and sequences, long-distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
Finally, a natural improvement would be to provide a graphical user interface to make the framework easy to use also for less technical users.

The field of literature review automation is maturing rapidly, and we expect an increasing use of such technologies to manage the ever-faster rate of scientific production.
We believe it is appreciable that a multiplicity of tools are being made available to let researchers and policymakers find the instrument that better fits their needs.\
We contribute to this field with an innovative framework that provide excellent performance and easy integration with existing systematic review pipelines.
The value of this work lies not only in the framework itself, which we provide as open-source software, but in the set of methodologies we developed to solve various SRA issues and that can be used to improve already existing solutions.\

>>>>

We propose a new integrated framework to help researchers collect and screen scientific publications that is characterised by high performance and versatility.
This framework joins the joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
This framework implements standard approaches and uses ad-hoc solutions to deal with common SRA issues.
By freely sharing the tool as an open-source R package and by following a modular design, we sought to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
The framework consists of four main components: 1) an integrated query-based citation search and management engine, 2) a Bayesian active machine learning-based citation classifier, and 3) a data-driven search query generation algorithm.\

The search engine module used by the framework is able to  automatically collect citation data from three well-known scientific databases (i.e., Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) asand to process manually downloaded results from both the two more databases (SCOPUS, EMBASE).
In comparison, most commercial or free SRH tools, rely on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing only on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
Mixing different databases is essential to obstain a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
in our results, 18.7% of the positive matches were found in only one of the different data sources, and no positive record was present in all the sources (data not shown).\
The framework online search algorithms are efficient enough to manage tens of thousands of search results, using various solutions to overcome the limitations of citation databases in terms of traffic and download quotas.
The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
The preliminary ordering allows to increase the positivity rate in the initial training set [@wallace2010active].\

For the framework's record classification module, we developed an active machine learning approach [@settles2009active; @miwa2014reducing] which is based on the best practices from other SRA studies but also brings further improvements at various levels.\
The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform text into input data for machine learning.
We did not include classical n-grams [@schonlau2017text];
rather we used network analysis to find non-consecutive, frequently associated terms, a generalisation of n-grams that relaxes the term adjacency assumption.
This approach can also be used to find term connections across parts of the records, e.g., whether a term has a different relevance when associated with a particular author.
The same technique, albeit with different parameters, was used to merge redundant terms to make the model estimation more efficient and reduce noise.\
The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text; @ohsawa1998keygraph] and is a valuable tool to extract semantic information that is not evident in one-word or consecutive n-gram models.\

The automatic classification algorithm is based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine].
Like other boosted trees algorithms [@hastie2009boosting], the BART method can explore complex non-linearities, perform variable selection, manage missing data while maintaining high predictive power.\
However, the Bayesian foundation of the method provides further benefits:
lower sensitivity to the choice of hyperparameters, natural regularisation through priors, and, most imporantly, predictive distributions as output instead of point-wise predictions [@soria2011belm; @joo2020being; @jospin2020hands].
By selecting relatively tight prior distributions, we discouraged overly deep trees, long tree sequences, and extreme predicted probabilities, this reducing the risk of overfitting.\
The algorithm runs multiple replications of the model and averages their predictive distributions creating an "ensemble";
this technique has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble], as we were able to confirm during the hyperparameter evaluation (Supplemental Material S2).
Ensembling reduces the uncertainty in the predictive distribution tails related to the randomness in the MCMC fit [@robert2004monte], generating a shift in the probability mass towards the distribution centre and stabilising it (i.e., reducing variance without impacting bias).
On the other hand, simply imposing more robust uninformative priors against extreme predictions would have reduced variance but also shifted the distribution towards a non-decision zone, increasing bias [@hansen2000bayesian].\
Since the number of model replications has a significant impact on computation times, we decided to use ten replicas, the lower value after which performance stabilised, as resulted from the evaluation of the hyperparameters (Supplemental Material S2, Fig. 2).\
We also investigated whether bootstrapping between replications [@breiman1996bagging] would improve performance;
however, contrary to theory [@diez2015diversity], it appeared to be slightly detrimental in our case (Supplemental Material S2, Fig. 2) compared to simple ensembling.\

A low rate of relevant matches (class imbalance) is typical for literature reviews [@sampson2011precision; @wallace2010semi; @o2015using], and a strong imbalance between positive and negative records can affect sensitivity [@khoshgoftaar2010comparing; @chawla2004special].\
To overcome this problem, we oversampled [@batista2004study] the positive records ten times before model fitting.
The hyperparameter analysis showed that the oversampling rate, together with model ensembling, was the parameter with the greatest impact on performance.\
A known risk with positive oversampling is the misclassification of negative records [@ramezankhani2016impact].
However, since all predicted positives in our approach are reviewed manually, we are always guaranteed to achieve 100% specificity/positive predictive value:
the only price for the increased sensitivity due to oversampling is a larger number of records to be reviewed.\
An alternative to oversampling would be to apply different weights and/or costs to the classes [@abd2013review; @diez2015diversity], but the BART implementation we used did not have this feature;
furthermore, using simple oversampling allows for broader compatibility with different modelling engines [@galar2011review; @roshan2020improvement].\
Finally, sorting the records by query term frequency (simple query ordering) produces a much higher rate of relevant records in the initial training set (17.2%) compared to the overall data (0.11%), which boosts the sensitivity of the model.\

One of the key innovations we have introduced is the concept of "uncertainty zone", thie implementation of which is possible thanks to the Bayesian foundation of the classification model.\
This construct guides the selection of records to be manually review and gets dynamically updated and reduced after each CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig. 1).\
This approach overcomes the usual requirement of dataset-specific hard thresholds in active machine learning, and also allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
The parameters required by our algorithm are general and non task-specific, like the PPD intervals based on which the uncertainty zone is built, and the maximum number of iterations without positive matches after which a session is concluded;
evaluation of the hyperparameters shows that the algorithm is robust against variations in these parameters and we expect the default values to perform well on most datasets.\
Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\

We assessed performance as the ability of the screening procedure (automatic classification plus manual review) to find the largest number of relevant records while requiring manual reviewing for as few of them as possible (i.e., sensitivity $\times$ efficiency).\
We avoided the classical out-of-sample approaches such as train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study; @james2013introduction].
Such methods primarily assume that the rate of positivity is the same on average in every possible random subset of the data [@tashman2000out];
this uniformity is broken by how the initial training set and the subsequent reviewed records are selected by the query-based ordering and active learning algorithm, resulting in a lower positivity rate in the unlabelled records (Fig. 2).
Moreover, a literature corpus is unique per search query/database combination, and therefore any out-of-sample performance estimate is not replicable since no new data can be acquired related to the current corpus.\
To estimate overall sensitivity, we instead applied simple Bayesian regression (surrogate model) to the manually reviewed data to abstract the classification model predictions and achieve a maximum entropy [@harremoes2001maximum] estimate of the number of missed positive matches among the unreviewed records in the whole dataset.
This simple surrogate model fitted the data very well ($R^2$ consistently above 97%) using only the lower 98% PrI boundary of the PPDs as predictor, indicating predictive consistency in the classification model.
The posterior predictive distribution of the surrogate model could be used to explore worse case scenarios in terms of sensitivity.\

By screening only a very small fraction of all records, our framework achieves very high sensitivity, bringing a meaningful reduction in workload.\
Based on the surrogate model, we predicted a predicted median sensitivity of 100% [93.5%, 100%] in the first session (screening 4.29% of records) and of 97.3% [73.8%, 100%] in the second (screening 1.34% of records):
efficiency increased significantly in the second session as only a few new positive matches were found;
however, given the large number of records, uncertainty about sensitivity also increased, as expected.\
Both results are above the usual performance in this field [@o2015using] and are in line with the average sensitivity of 92% estimated after human-only screening [@edwards2002identification].
In one interesting case, the model detected a human-caused misclassification error, demonstrating its robustness and value as a second screener, a role already suggested for SRA tools in previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].
Although "simple query ordering" concentrated most relevant matches in the first 20-25 thousand records, without the tool support the remaining relevant records would have been missed withouth manually screeening almost the entire dataset.\

The model required ~5-20 minutes per iteration to perform the predictions in session 1 (17,755 documents) and 20-40 minutes in session 2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM, 2014 laptop;
including manual record review, one session required 1-3 days of work, for a total of 1-2 weeks for the whole process (including record collection).
This is a considerable time saving compared to the several months typically required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating].
To our knowledge, the amount of data processed (~100,000 records) was larger than what is typical of most SRA studies [@o2015using; @olorisade2016critical], highlighting the scalability of the tool in real-world scenarios.\

The last module of our framework is an algorithm for data-driven search query generation.
Generating an efficient and effective search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching];
it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of records to be reviewed.
Our solution combines a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD, with a human review step and an efficiency-driven query builder.
The aim is to generate a new search query to help find records missed in the first search session.
The generated query did indeed to retrieve a few more relevant records that were not found in session 1, but at the cost of a significant increase in the number of documents.\
An interesting aspect of this feature is that it provides a human-readable overview of the classification rules learned by the classification model, showing which combination of terms was particularly relevant and even spotting authors and geographical locations associated with the study topic.
The generated query, therefore, served also as a means for machine learning explainability [@bhatt2020machine; @burkart2021survey], useful for understanding and detecting biases in black-box classification algorithms [@malhi2020explainable];
explainability is often required or even legally mandatory for high-stake machine learning applications [@bibal2021legal; @bibal2020impact].\
It is important to note that this process is entirely data-driven.
The algorithm is only aware of the "world" defined by the dataset used as input, which is generated by a specific search query focused on a particular topic.
Therefore, the new query may not be specific enough when applied to an unbounded search domain, and may return an unmanageable amount of unrelated results.
The solution we found was to add another component to the query, specifying the general topic (antimicrobial resistance and healthcare-associated infections) of our research.\

As mentioned early, our framework builds on modularity.
We have designed it in such a way that full independence of the main modules can be easily implemented in future iterations;
it will be possible for users to add custom features such as citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
We consider such interoperability to be extremely relevant:
the main strength of our tool lies in the composition of many solutions such as the idea of Bayesian active machine learning and the exploit of the derived uncertainty in defining the records needing human review.\
However, each components could benefit considerably from the recent improvements in text mining and machine learning.\
For example, our text processing approach, based on the "boolean bag-of-words" paradigm, is quite simple, and indeed could be improved by more nuanced text representations.
It might be considered whether feature transformations such as TF-IDF [@baeza1999modern; @ananiadou2006text] could be advantageous, although we hypothesise that tree-based classification algorithms like BART are robust enough not to require such operations.
Instead, it might be worth exploring the application of word embedding:
this technique transforms terms into semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding; @minaee2021deep] and could be used to reduce noise by merging different terms that are semantically similar and enhance signal by distinguishing identical terms with different meaning given the context.
Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] or graph-of-word techniques [@ohsawa1998keygraph; @rousseau2015graph] to extract topics to expand the feature space.\
Our classification algorithm is applicable with any Bayesian supervised machine learning method that provides full PPDs;
therefore, alternative classification models, such as Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian], could be evaluated.
It would be even more interesting to test advanced learning algorithms that go beyond the bag-of-words approach and take into consideration higher-level features in the text such as term context and sequences, long-distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], provided that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
Finally, a natural improvement would be to provide a graphical user interface to make the framework easy to use also for less technical users.

The field of literature review automation is evolving rapidly, and we anticipate an increasing use of such technologies to address the accelerating pace of scientific production.
We believe it is encouraging that a wide variety of tools are being made available to allow researchers and policymakers find the approach that best fits their needs.\
We are contributing to this field with an innovative framework that provides excellent performance and easy integration with existing systematic review pipelines.
The value of this work lies not only in the framework itself, which we make available as open-source software, but also in the set of methodologies we developed to solve various SRA issues and which can also be used to improve already existing solutions.\

### 2022-02-19 Manuscript/Manuscript_Introduction.Rmd
added extra line before references
English proof reading and better number formatting

This is especially true for biomedical research, a trend further increased by the COVID-19 pandemic, thanks to faster article' processing time by publishers and the diffusion of preprint databases' usage [@aviv2021publication; @horbach2020pandemic; @hoy2020rise].
Consequently, it gets harder for researchers and practitioners to stay up-to-date on the latest findings in their field.
Secondary research is of paramount relevance in this scenario, providing valuable summaries of the latest research results, but is getting ever more demanding in terms of time and human resources [@allen1999estimating; @borah2017analysis; @cohen2010evidence; @bastian2010seventy].\

@@

First, relevant published research needs to be collected from scientific databases through appropriately built search queries (retrieval phase); secondly, the acquired scientific citations need to be screened, selecting only those relevant to the topic (appraisal phase) [@bannach2019machine; @tsafnat2014systematic; @higgins2019cochrane].\
The construction of search queries is a complex task [@lefebvre2011searching; @hammerstrom2010searching], requiring both domain and some knowledge of the databases' query languages;
the goal is to produce a set of results containing all relevant articles (high sensitivity) while keeping the total number low (high specificity), focusing on the first aspect at the cost of the second [@hammerstrom2010searching].

@@

this approach is complicated by limits in the number of records that can be downloaded at once and the necessity to harmonise different formats and resolve record duplication [@marshall2015systematic].\
The citation screening phase is usually the more resource-demanding task of a systematic review:
even with appropriately built search queries, the returned results easily range in the tens of thousands of which just a small fraction is actually relevant [@lefebvre2011searching].
It was estimated that labelling 10,000 publications may take as much as 40 weeks of work and that the average clinical systematic review takes 63 weeks to be completed [@bannach2019machine; @borah2017analysis; @allen1999estimating].
A consequence is that often systematic reviews are already outdated once they are published [@beller2013systematic].\

@@

Through the application of natural language processing (NLP), it is possible to transform free text into quantitative features, with various levels of abstraction and generalisation [@ananiadou2006text; @cohen2008getting];
with machine learning, such text-derived data can be used to map and reproduce human judgment, automating the citation screening [@ikonomakis2005text].\
The automation of systematic reviews has been ripe with improvements in the last years [@ananiadou2009supporting; @o2015using; @tsafnat2013automation; @jonnalagadda2015automating], and it is possible to foresee that it is going to become the standard approach in the field [@beller2018making], with many solutions already being turned into commercial and free-to-use tools [see @marshall2015systematic, table 1].\
In this manuscript we present an open source, production-ready framework which further contributes to the state-of-the-art in systematic review automation (SRA) and helpers (SRH) tools.
We improve the "retrieval phase" by providing a unified framework for the automatic collection and management of scientific literature from multiple online sources.
For the citation screening (appraisal) phase, we built an active machine learning-based [@settles2009active, @miwa2014reducing; @miwa2014reducing] protocol, which exploits a Bayesian framework to efficiently identify potentially relevant documents that require human review while automatically screening-out the large majority of clearly non-relevant ones;
the algorithm then uses human reviews to iteratively increase classification accuracy.
Finally, we included a tool to generate new search queries given an already labelled citation data set, in order to identify relevant research possibly missed by human-made queries.\
We tested the framework in the retrieval and appraisal phases of an example topic of interest for our group:

@@

We give an overview of the framework in the Methods section;
in the Result section, we show the framework outputs and performance once applied to the example topic;
in the Discussion, we lay out the methodological justification behind the different components and features of the framework.

>>>>

This is especially true for biomedical research, a trend further accelerated by the COVID-19 pandemic, thanks to faster article' processing time by publishers and the greater use of preprint databases [@aviv2021publication; @horbach2020pandemic; @hoy2020rise].
Consequently, it has become harder for researchers and practitioners to stay up to date on the latest findings in their field.
Secondary research is of paramount importance in this scenario in that it provides valuable summaries of the latest research results;
however, it is becoming ever more challenging in terms of time and human resources required [@allen1999estimating; @borah2017analysis; @cohen2010evidence; @bastian2010seventy].\

@@

First, relevant published research must be collected from scientific databases using appropriately built search queries (retrieval phase); secondly, the scientific citations collected must be screened, selecting only those that are relevant to the topic (appraisal phase) [@bannach2019machine; @tsafnat2014systematic; @higgins2019cochrane].\
Search queries construction is a complex task [@lefebvre2011searching; @hammerstrom2010searching], requiring both expertise in the scientific field of interest and some knowledge of the database query languages.
The goal is to obtain a set of results that contains all relevant articles (high sensitivity) while keeping the total number of records low (high specificity),
possibly focusing on the first at the expense of the second [@hammerstrom2010searching].\

@@

this approach is complicated by limits to the number of records that can be downloaded at any one time and the need to harmonise different formats and resolve record duplication [@marshall2015systematic].\
The citation screening phase is usually the more resource-demanding task in a systematic review:
even with appropriately built search queries, the results may easily range in the tens of thousands, of which just a small fraction are actually relevant [@lefebvre2011searching].
It has been estimated that labelling 10,000 publications can take up to 40 weeks of work and that the average clinical systematic review takes 63 weeks to complete [@bannach2019machine; @borah2017analysis; @allen1999estimating].
A consequence of this is systematic reviews are often already out-of-date by the time they are published [@beller2013systematic].\

@@

By applying natural language processing (NLP), it is possible to transform free text into quantitative features, with various levels of abstraction and generalisation [@ananiadou2006text; @cohen2008getting];
using machine learning, such text-derived data can be used to map and reproduce human judgment, automating the screening of citations [@ikonomakis2005text].\
Automation of systematic reviews has made significant improvements in the last years [@ananiadou2009supporting; @o2015using; @tsafnat2013automation; @jonnalagadda2015automating], and it is possible foreseeable that it will become the standard approach in the field [@beller2018making], with many solutions already being implemented into commercial or free-to-use tools [see @marshall2015systematic, table 1].\
In this manuscript, we present an open source, production-ready framework that further contributes to the state-of-the-art in systematic review automation (SRA) and helpers (SRH) tools.
We improve the "retrieval phase" by providing a unified framework for the automated collection and management of scientific literature from multiple online sources.
For the citation screening (appraisal) phase, we built an active machine learning-based protocol [@settles2009active; @miwa2014reducing],
which utilises a Bayesian framework to efficiently identify potentially relevant documents that require human review, while automatically screening-out the vast majority of clearly non-relevant ones;
the algorithm then requires human review to iteratively increase classification accuracy.
Finally, we included a tool to generate new search queries based on an already labelled citation data set, to identify relevant research that may possibly have been missed by manually-made queries.\
We tested the framework in the retrieval and appraisal phases of an example topic of interest to our group:

@@

In the Methods, we give an overview of the framework,
in the Result, we show the outputs and performance of the framework applied to the example topic,
and in the Discussion, we explain the methodological rationale for the different components and features of the framework.\
